Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-02-28 additional_files/manuscript.tex
Remove vg results from signal plots

% Defining a new command for signal plot figures
\newcommand{\signalplot}[4]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_signal}
	\caption[Zoomed-in Manhattan plots of the #3 locus]{Zoomed-in Manhattan plots of signals detected by the GWAS analysis of #2 at the #3 locus using four genotype datasets:
	(b) Platypus (SNPs and indels), (c) vg (SVs), (d) Paragraph (SVs), (e) \emph{k}-mers presence/absence.
	Panel (a) shows gene models over the genomic interval.
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	#4
	Gray shaded rectangles indicate the region delimited by the top 5\% (Paragraph and vg) or top 1\% (Platypus and \emph{k}-mers) associations in the signal region.
	In the case of Platypus, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	}
	\label{#1_signal}
\end{cfigure}

>>>>

% Defining a new command for signal plot figures
\newcommand{\signalplot}[4]{
\begin{cfigure}
	\includegraphics[width = 5.8in]{#1_signal}
	\caption[Zoomed-in Manhattan plots of the #3 locus]{Zoomed-in Manhattan plots of signals detected by the GWAS analysis of #2 at the #3 locus using three genotype datasets:
	(b) Platypus (SNPs and indels), (c) Paragraph (SVs), (d) \emph{k}-mers presence/absence.
	Panel (a) shows gene models over the genomic interval.
	Horizontal dotted lines indicate the 5\% family-wise error-rate significance threshold determined from a randomization approach.
	#4
	Gray shaded rectangles indicate the region delimited by the top 5\% (Paragraph) or top 1\% (Platypus and \emph{k}-mers) associations in the signal region.
	In the case of Platypus, blue points denote markers used in the original analysis, whereas red points denote points that had originally been pruned but whose
	\emph{p}-values were computed after signal discovery.
	}
	\label{#1_signal}
\end{cfigure}
